5 slides to convince you that it's endogenous TFP

### 2018-02-01 Latex/Basu_propositions/propositions.tex
updated basu slides
updated basu presentation with new notation

\title{3 slides to convince you that it's endogenous TFP}

@@

Final goods firm (GE)
\begin{align*}
\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
 & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
 & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
\end{align*}

IT-producing firm (Google)
\begin{align*}
\max_{K^{I}_t(s), L^{I}_t(s)} I^{IT}_t(s) = P^{IT}_t S_t \lambda_t F(K^I_t(s), L^I_t(s)) -w_t L^I_t(s) - R_t K^I_t(s)
\end{align*}

@@

A news shock is $S_{t+k} \uparrow$ for some positive $k$.

@@

\begin{align*}
\frac{\dot{A}}{A} = & \frac{\dot{Y}}{Y} - \alpha \frac{\dot{K^f}}{K^f} - \beta \frac{\dot{L^f}}{L^f} - (1-\alpha - \beta) \frac{\dot{K^{IT}}}{K^{IT}} \\
= & \frac{\dot{S}}{S} + \frac{\dot{\Psi}}{\Psi} + \gamma \frac{\dot{K^{IT}}}{K^{IT}}
\end{align*}

TFP consists of an exogenous, common technology process $S$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology. 
\end{frame}
%%%%%%%%%%%%%%%%%

@@

\begin{align*}
R_t = & \alpha \frac{Y_t(s)}{K^f_t(s)} P^C_t = S_t \lambda_t F_k P^{IT}_t \\
\Leftrightarrow \frac{P^{IT}_t }{P^{C}_t } = & \alpha \frac{K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}S_t \Psi_t (K^{IT}_t)^{\gamma} }{K^f_t(s)} \frac{1}{S_t \lambda_t F_k}
\end{align*}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{+1 slide: evidence that $\gamma \neq 0$, i.e. that GPTs show up as spillovers}

>>>>

\title{5 slides to convince you that it's endogenous TFP}

@@

Final goods firm (GE)
\begin{align*}
\max_{K_{1,t}(s), L_{1,t}(s), S^{IT}_t(s) } Y_t(s) =  & K_{1,t}(s)^{\alpha}L_{1,t}(s)^{\beta}S^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_{1,t}(s) -R_tK_{1,t}(s) -P^{IT}_t IT_t(s) \\
 & \text{where} \; S^{IT}_t(s) =  (1-\delta^{IT})S^{IT}_{t-1} + IT_t \\
 &  \; A_t =  \eta_t \Psi_t (G(S^{IT}_t,S^{IT}_{t-1},\dots))^{\gamma} \\
 &  \; G(S^{IT}_t,S^{IT}_{t-1},\dots) = \zeta_1 S_t^{IT} + \zeta_2 S^{IT}_{t-1} + \dots \\
  & \text{and} \; \sum_{i=1}^{N} \zeta_i = 1
\end{align*}

IT-producing firm (Google)
\begin{align*}
\max_{K_{2,t}(s), L_{2,t}(s)} IT_t(s) = P^{IT}_t \eta_t \lambda_t F(K_{2,t}(s), L_{2,t}(s)) -w_t L_{2,t}(s) - R_t K_{2,t}(s)
\end{align*}

@@

A news shock is $\eta_{t+k} \uparrow$ for some positive $k$.

@@

\begin{align*}
\frac{\dot{A}}{A} = & \frac{\dot{Y}}{Y} - \alpha \frac{\dot{K_1}}{K_1} - \beta \frac{\dot{L_1}}{L_1} - (1-\alpha - \beta) \frac{\dot{S^{IT}}}{S^{IT}} \\
= & \frac{\dot{\eta}}{\eta} + \frac{\dot{\Psi}}{\Psi} + \gamma \frac{\dot{G}(S^{IT},\dots)}{G(S^{IT},\dots)}
\end{align*}

TFP consists of an exogenous, common technology process $\eta$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology. 
\end{frame}
%%%%%%%%%%%%%%%%%

@@

\begin{align*}
R_t = & \alpha \frac{Y_t(s)}{K_{1,t}(s)} P^C_t = \eta_t \lambda_t F_k P^{IT}_t \\
\Leftrightarrow \frac{P^{IT}_t }{P^{C}_t } = & \alpha \frac{K_{1,t}(s)^{\alpha}L_{1,t}(s)^{\beta}S^{IT}_t(s)^{1-\alpha - \beta}\eta_t \Psi_t (S^{IT}_t)^{\gamma} }{K_{1,t}(s)} \frac{1}{\eta_t \lambda_t F_k}
\end{align*}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Evidence that $\gamma \neq 0$; GPTs show up as spillovers}
